### 2014-10-28 ThesisJo/derivations.tex
la2pdf commit - 2014:10:28	17:07:58	(Tue28.Oct)

Equation (\ref{wave_eq_mass_conservation}), (\ref{wave_eq_euler}) and (\ref{wave_eq_sound_pressure}) are non-linear, but can be linearized by assuming each quantity to be a steady-state, time-independent value plus a fluctuation term:
%
\begin{align}
p = p_0 + p'  \qquad\qquad \rho = \rho_0 + \rho' \qquad\qquad \v = \v_0 + \v'
\end{align}
%
Taylor expanding (\ref{wave_eq_sound_pressure}) around zero yields:
%
\begin{align}
p(\rho) = p_0 + \frac{\partial p}{\partial\rho}(\rho-\rho_0) + \frac{1}{2}\frac{\partial^2 p}{\partial\rho^2}(\rho-\rho_0)^2 + \dots\label{wave_eq_sound_taylor_full}
\end{align}
%
and if we can assume the first order to be sufficient we get:
%
\begin{align}
p(\rho) = p_0 + \frac{\partial p}{\partial\rho}(\rho-\rho_0)\label{wave_eq_sound_taylor_first}
\end{align}

>>>>

\subsection{Linearization}

Equation (\ref{wave_eq_mass_conservation}), (\ref{wave_eq_euler}) and (\ref{wave_eq_sound_pressure}) are non-linear, but can be linearized by assuming each quantity to be a steady-state, time-independent value plus a fluctuation term:
%
\begin{align}
p = p_0 + p'  \qquad\qquad \rho = \rho_0 + \rho' \qquad\qquad \v = \v_0 + \v'
\end{align}
%
Taylor expanding (\ref{wave_eq_sound_pressure}) around zero yields:
%
\begin{align}
p(\rho) = p_0 + \frac{\partial p}{\partial\rho}(\rho-\rho_0) + \frac{1}{2}\frac{\partial^2 p}{\partial\rho^2}(\rho-\rho_0)^2 + \dots\label{wave_eq_sound_taylor_full}
\end{align}
%
Assuming a linear relationship between changes in pressure and volume the pressure perturbation term is simply:
%
\begin{align}
p' = \frac{\partial p}{\partial\rho}(\rho-\rho_0) = \frac{\partial p}{\partial\rho}\rho' = c^2\rho'. \label{wave_eq_sound_taylor_first}
\end{align}
%
When treating the Euler equation the same way we obtain:
%
\begin{align}
-\nabla (p_0 + p') &= (\rho_0 + \rho') \Big(\frac{\partial(\v_0 + \v')}{\partial t} + (\v_0 + \v')\cdot\nabla(\v_0 + \v')\Big) \nn
-\nabla p' &= (\rho_0 + \rho') \Big(\frac{\partial\v'}{\partial t} + \v'\cdot\nabla\v'\Big) \nn
\end{align}
%
When acceleration mainly depends on time, and the pressure fluctuations are relatively small,
%
\begin{align}
\frac{\partial\v'}{\partial t} >> \v'\cdot\nabla\v' \qquad\qquad\text{and}\qquad\qquad \rho_0 >> \rho',
\end{align}
%
then
%
\begin{align}
-\nabla p' &= \rho_0 \frac{\partial\v'}{\partial t}.
\end{align}
%
Finally, for the mass conservation we have:
%
\begin{align}
\frac{\partial(\rho_0 + \rho')}{\partial t} = -\nabla \cdot ((\rho_0 + \rho')(\v_0 + \v')). \label{wave_eq_mass_conservation}
\end{align}
